Individual Variation in Animal Movement and Effects on Seed Dispersal Distance

### 2021-01-07 paper/paper.Rmd
Figure 1 updates
Figures updates

```{r}
set.seed(5)
library(ggplot2)
library(aracari)
library(cowplot)

@@

# ALL
plot_grid(p1, p2, p3, p4, p5, p6, labels = LETTERS[1:6], nrow = 3)

>>>>

```{r eval = TRUE, fig.width=6}
set.seed(5)
library(ggplot2)
library(aracari)
library(cowplot)

@@

# ALL
plot_grid(p1, p2, p3, p4, p5, p6, labels = LETTERS[1:6], label_size = 10, nrow = 3)
